Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-21 final_metrics_analysis.Rmd
add word charge

```{python wordcloud}
text = " ".join(charge for charge in df_viz.c_charge_desc)
stopwords = set(STOPWORDS)
stopwords.update(["arrest", "case"])
wordcloud = WordCloud(stopwords=stopwords, background_color="white").generate(text)
```

>>>>

```{python wordcloud}
text = " ".join(charge for charge in df_viz.c_charge_desc)
stopwords = set(STOPWORDS)
stopwords.update(["arrest", "case", "charge"])
wordcloud = WordCloud(stopwords=stopwords, background_color="white").generate(text)
```
